Gozde and Liora Replication Code

### 2015-04-28 replication project.Rmd
Updated and combined replication code with extension

Note: Please refer to saved files in our repository for images from the article. Also please refer to the table and figures (Table 1, Figure 1, 2) in the repository. Image scales are rearranged in saved versions. Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood. Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables.

#The paper
Kai Arzheimer, "Contextual Factors and the Extreme Right Vote in Western Europe, 1980-2002"25548117.pdf
This article attempts to answer the “twin question of why the extreme right support is so unstable within many countries over time, and why these parties are so weak in many West European countries.” Authors conduct a multi-level analysis, combining data on macro-level contextual variables (unemployment, immigration, and welfare benefits) with individual-level variables (sociodemographic factors and attitudes).

@@

#The model 
The article uses a logistic multi-level model via Penalized Quasi-Likelihood. The dependent variable is vote intention for an extreme right party, which is assumed to be binomially distributed.

@@

# Figure 2, graph 1
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)

@@

grid.arrange(graph_3, graph_4, ncol = 1)
# Better scaled versions - not combined
graph_3
graph_4
`
```

@@

@@

log.odds <- model_1$fitted.values # Create a vector with log-odd values
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
plot_model1
```

@@

log.odds <- model_2$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
plot_model2
```

>>>>

Note: Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood. Finally, we were unfortunately not able to reproduce the last two figures that showed the joint impact of more than 2 variables.

#The paper
Kai Arzheimer, "Contextual Factors and the Extreme Right Vote in Western Europe, 1980-2002"25548117.pdf
This article attempts to answer the “twin question of why the extreme right support is so unstable within many countries over time, and why these parties are so weak in many West European countries.” The author conduct a multi-level analysis, combining data on macro-level contextual variables (unemployment, immigration, and welfare benefits) with individual-level variables (sociodemographic factors and attitudes). It concludes that although the contextual factors are positively correlated with the intention to vote for an extreme-right party, they don't seem to reinforce each other (i.e. as unemployment levels rise, the effect of immigration does not increase but rather declines).

@@

#The model 
The article uses a multi-level logistic model via Penalized Quasi-Likelihood. The dependent variable is vote intention for an extreme right party, which is assumed to be binomially distributed.

@@

```{r}
# Figure 2, graph 1
# Create vector with possible values for salience
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by = .1) 
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)

@@

grid.arrange(graph_3, graph_4, ncol = 1)
# Better scaled versions - not combined
graph_3
graph_4
```

@@

Run necessary packages and load data (Source: Arzheimer dataverse)

@@

log.odds <- model_1$fitted.values # Create a vector with log-odd values
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

![Model 1](figures/SP.Model1.png)

@@

log.odds <- model_2$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

![Model 2](figures/SP.model2.png)
